\chapter{Performance Modeling and Analysis}
\label{ch:perfmodel}
\index{PerfModel!Performance Modeling}
\chaptertoc
\noindent

Generally, work-stealing or reactive load balancing make decisions based on the current execution status at runtime. Their decisions take balancing operation and task migration into account. Balancing operations denote checking imbalance status and exchanging information, while task migration denotes moving tasks from one process to another. These can affect the overall performance. Therefore, it is difficult to determine efficiency as well as performance of balancing decisions before running applications. We address this with a performance model.\\

Regarding the previous works, several performance models for work stealing have been proposed, such as \cite{gast2021analysis}, \cite{tchiboukdjian2010tighter}, \cite{hayat2004dyntimemodelws}. The authors use discrete-time models to address the behavior of work stealing, mainly focusing on the constraints of communication latency when tasks are migrated. In their work, the latency is considered a constant, and all tasks have the same overhead in migration. However, we show that tasks can be different in type and data size in terms of HPC as well as task-based parallel applications. Therefore, communication latency alone cannot model balancing behavior very well in practice, and these models are not suitable in our context. To analyze how the previous models are built, we do not go into detail in this chapter because work stealing has passive behavior from the view of load balancing operations, and it is also extensively analyzed with the existing models mentioned above. Therefore, we summarize one of the most related models in Appendix \ref{App_A:Perf_Model}.\\

In constrast, we introduce a new performance model, mainly focusing on the behaviors of reactive load balancing. We assume a given imbalance context along with the overhead of balancing operations and task migration, where the given imbalance context is already mentioned in Subsection \ref{subsec:dlb}. The overhead is bounded by two metrics, latency ($\lambda$) and delay time ($d$). In detail, the input and output of our model can be simplified as follows.
\begin{itemize}
	\item The main influence inputs include the number of involved processes, number of tasks in total, number of slowdown processes, slowdown factors of corresponding processes, and the overhead for balancing operations as well as task migration (delay time).
	\item The output indicates the performance of modeled and simulated cases in execution time, number of local and migrated (offloaded) tasks on each process.
\end{itemize}

The model is leveraged to design a simulator, where its output can be used to analyze the bound of dynamic load balancing approaches among different scenarios.\\

An overview of this chapter is as follows: Section \ref{sec:NewModel-ReactLB} presents the performance model concerning reactive load balancing, followed by an introduction to the associated simulator and model evaluation in Section \ref{sec:Model-Simulation-Evaluation}. Additionally, Section \ref{sec:Idea-Proactive-LB} highlights the idea of proactive load balancing, which is grounded in our performance model.

\input{content/PerfModel-NewModel-in-HPC}

\input{content/PerfModel-Simulation-Evaluation}

\input{content/PerfModel-TowardProactIdea}

%\input{content/PerfModel-RefModel-for-WS}

%\input{content/PerfModel-Evaluation}

% Chapter \ref{ch:perfmodel}
% Our work looks at a higher level of task migration when the task data can be affected by transmission time or delay ($d$). The idea is to understand how impacts dynamic balancing operations under a certain imbalance level and a delay when tasks are migrated.
% $d$ at a time depends on latency and bandwidth. Transmission time or delay is the time of transmitting an entire message between two compute nodes. If there are no conflicts, the delay can be computed by $d(S) = \lambda + S/B$, where $S$ denotes the message size, $\lambda$ is the constant latency, and $B$ is the network bandwidth. Indeed, the message size depends on how tasks are simplified, which could be task argument or output data. Our model supports building a simulator, which gets the initial task distribution and related communication constraints as input.\\

%Delay is calculated by the latency and bandwidth at a period plus the size of migrated tasks. Hence, the delay time can more or less affect the load balance performance. In detail, we aim to clarify step by step the following ideas,
%\begin{itemize}
%	\item Analyze related models of work stealing with and without communication latency.
%	\item Introduce a proposed model with delay time in task migration. This model can be used to analyze work stealing and reactive task offloading.
%	\item Introduce a corresponding simulator to investigate the bound of these existing solutions and constraints as mentioned
%	\item Explain further the idea of proactive load balancing.
%\end{itemize}